Article data analysis

### 2018-10-24 notebooks/article_notebook.Rmd
updated figure with legend

## Total combinations
```{r}
test <- acquired_report %>%
  left_join(mut_quant[c("gyrA","gyrB","parC","parE","id")], by = "id") %>%
  left_join(mut_report[c("marR","id")], by = "id") %>%
  left_join(mic_data[c("id","CIP","NAL")], by = "id") %>%
  left_join(isolate_data[c("id","species")], by = "id") %>%
  select(-id) %>%
  group_by_at(vars(-c(CIP, NAL))) %>%
  summarise(CIP = ifelse(min(as.numeric(CIP)) == max(as.numeric(CIP)),
                         as.character(median(as.numeric(CIP))),
                         paste(min(as.numeric(CIP)), max(as.numeric(CIP)), sep = " - ")),
            NAL = ifelse(min(as.numeric(NAL)) == max(as.numeric(NAL)),
                         as.character(median(as.numeric(NAL))),
                         paste(min(as.numeric(NAL)), max(as.numeric(NAL)), sep = " - ")),
            n = n()) %>%
  rowwise() %>%
  mutate(Total = 285,
         Percent = round(n/Total * 100,1),
         lwr = round(get_binCI(n, Total)[1],1),
         upr = round(get_binCI(n, Total)[2],1),
         "95 % CI" = paste("[", lwr, "-", upr, "]")) %>%
  select(-c(lwr, upr, Total))
```

@@

p1 <- ggplot(total_df2, aes(reorder(gene, type), factor(CIP), fill = perc))+
  geom_tile(color = "grey70")+
  scale_fill_viridis(option = "A",
                     begin = 0.1)+
  guides(fill = FALSE)+
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.3, size = 14),
        axis.text.y = element_text(size = 14),
        axis.title.x = element_blank(),
        axis.title.y = element_text(size = 16),
        strip.background = element_rect(colour = "black", fill = "grey70"),
        strip.text = element_text(size = 14),
        plot.margin = unit(c(0,0,0,0), "cm"))+
  labs(y = "CIP MIC")+
  facet_wrap(~species, ncol = 1)+
  coord_fixed()

@@

p2 <- ggplot(nplot_data, aes(factor(CIP), n))+
  geom_col()+
  theme(axis.title = element_blank(),
        axis.text.y = element_blank(),
        axis.text.x = element_text(size = 14),
        axis.ticks.y = element_blank(),
        strip.text = element_text(size = 14),
        strip.background = element_rect(colour = "black", fill = "grey70"),
        plot.margin = unit(c(0,0,-10,0), "cm"))+
  facet_wrap(~species, ncol = 1)+
  coord_flip()

>>>>

## Total combinations
```{r}
acquired_report %>%
  left_join(mut_quant[c("gyrA","gyrB","parC","parE","id")], by = "id") %>%
  left_join(mut_report[c("marR","id")], by = "id") %>%
  left_join(mic_data[c("id","CIP","NAL")], by = "id") %>%
  left_join(isolate_data[c("id","species")], by = "id") %>%
  select(-id) %>%
  group_by_at(vars(-c(CIP, NAL))) %>%
  summarise(CIP = ifelse(min(as.numeric(CIP)) == max(as.numeric(CIP)),
                         as.character(median(as.numeric(CIP))),
                         paste(min(as.numeric(CIP)), max(as.numeric(CIP)), sep = " - ")),
            NAL = ifelse(min(as.numeric(NAL)) == max(as.numeric(NAL)),
                         as.character(median(as.numeric(NAL))),
                         paste(min(as.numeric(NAL)), max(as.numeric(NAL)), sep = " - ")),
            n = n()) %>%
  rowwise() %>%
  mutate(Total = 285,
         Percent = round(n/Total * 100,1),
         lwr = round(get_binCI(n, Total)[1],1),
         upr = round(get_binCI(n, Total)[2],1),
         "95 % CI" = paste("[", lwr, "-", upr, "]")) %>%
  select(-c(lwr, upr, Total))
```

@@

p1 <- ggplot(total_df2, aes(reorder(gene, type), factor(CIP), fill = perc))+
  geom_tile(color = "grey70")+
  scale_fill_viridis(option = "A",
                     begin = 0.1,
                     guide = guide_colorbar(barheight = 15,
                                            barwidth = 1,
                                            label.position = "left",
                                            label.hjust = 0.5,
                                            label.vjust = 0.3,
                                            ticks = TRUE))+
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.3, size = 18),
        axis.text.y = element_text(size = 18),
        axis.title.x = element_blank(),
        axis.title.y = element_text(size = 20),
        strip.background = element_rect(colour = "black", fill = "grey70"),
        strip.text = element_text(size = 18),
        legend.position = "left",
        legend.title = element_blank(),
        legend.text = element_text(size = 14),
        plot.margin = unit(c(0,0,0,0), "cm"))+
  labs(y = "CIP MIC")+
  facet_wrap(~species, ncol = 1)+
  coord_fixed()

@@

p2 <- ggplot(nplot_data, aes(factor(CIP), n))+
  geom_col()+
  theme(axis.title = element_blank(),
        axis.text.y = element_blank(),
        axis.text.x = element_text(size = 18),
        axis.ticks.y = element_blank(),
        strip.text = element_text(size = 18),
        strip.background = element_rect(colour = "black", fill = "grey70"),
        plot.margin = unit(c(0,0,-10,0), "cm"))+
  facet_wrap(~species, ncol = 1)+
  coord_flip()
